### 2012-11-29 paper/paper.tex
Add paper

\documentclass[11pt,letterpaper,notitlepage]{article}

\usepackage{fullpage}
\usepackage{enumerate}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{paralist}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{clrscode3e}
\usepackage{appendix}
\usepackage{framed}
\usepackage{graphicx}

\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=black
}

\title{An Investigation of the SPDY Protocol}
\date{\today}
\author{Brian Stack\thanks{ bis12@case.edu, Case Western Reserve University,
Cleveland, OH 44106}}

\begin{document}
\maketitle
\setcounter{tocdepth}{1}
\tableofcontents 
\begin{abstract}
The HTTP/1.1 specification is now well over a decade old~\cite{rfc2616}. Updates
have been constantly made to the specification, in an attempt to clear up
discrepancies or clarify murky parts of the document.  The most recent attempt
at this was made as recently as April of 2012~\cite{rfc6585}.  Even so, as the web grows
and changes, the venerable spec is beginning to show its age.  Companies such as
Google and Facebook who serve massive portions of the daily web traffic are
pushing the limit of HTTP performance, mostly due to the outdated design
assumptions made during the original specification of the protocol.  In March of
2012, httpbis (the IETF's HTTP working group) updated their charter to
include a directive of creating a new specification -- HTTP/2.0.  One of the
most likely starting points for the new protocol will be Google's
SPDY~\cite{spdyspec}.  This paper will inspect this protocol to analyze its
performance and weigh it against the design compromises it makes in order to
help decide whether or not this is a good direction for the HTTP specification
to go.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The most recent httbis working group charter includes the following
goals~\cite{httpbis-charter}:
\begin{itemize}
\item Significantly improve performance in common use cases
\item Make more efficient use of network resources
\item Must be deployable on the current internet
\item Maintain ease of deployment
\item Updated security to modern standards
\end{itemize}
The current self-imposed deadline for the spec is July
2013~\cite{httpbis-charter}.  There are currently 3 likely starting points for
the specification that have been proposed. They will be covered beginning in
\S\ref{sec:intro/opensource}. The most important part of the goals that is not
explicitly mentioned is that these proposals must maintain semantic equivalence
with the currently implemented HTTP specification; changes may only be made to
the method in which these request/response pairs are transmitted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Problem Statement}
\label{sec:intro/problem}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The web has developed to the point where HTTP/1.1 is no longer sufficient to
architect our major web applications. The basic semantic meaning is excellent,
and is the foundation of the web, but certain engineering considerations must be
taken into account in order to improve the protocol.  One proposal for this next
generation protocol is Google's SPDY~\cite{spdyspec}.  Most agree that this protocol will
be optimal for Google, but the question remains whether or not this will be an
improvement for the vast majority of the web.  Does the rather drastic increase
in complexity pay off in the general case, and is it worth the added cost in
terms of development time to support this protocol everywhere?

This project sets out to answer that question in two fashions.  First with an in
depth examination of what is the limiting factor of current HTTP/1.1 including a
review of literature in the area.  More importantly, an experiment will be
conducted to determine empirically how much of an improvement is seen when using
SPDY rather than HTTP.  The experiment is proposed in \S\ref{sec:project}. The
remainder of this section will give a quick overview of the proposals to replace
HTTP/1.1.

% TODO: Expand on these for the full paper!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Network-Friendly}
\label{sec:intro/opensource}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This proposal comes from a group of open-source developers without any strict
ties to a company or organization otherwise.  It is quite different from the
other two proposals because it is looking at the problem from another angle.
The four main ideas in this proposal are~\cite{friendly}
\begin{itemize}
\item Binary encoding of header fields\footnote{This might be expected
considering that one of the primary authors of this proposal is the creator of
the Varnish Cache \url{https://www.varnish-cache.org/} which must inspect the
header fields of incoming requests.}
\item Grouping of common header fields allowing for reduced header size when
repeated requests are made.
\item Multiplexing of request and response.  This is something shared in common
with all three of the currently viable proposals.
\item A layering model that is easier for intermediaries like Varnish to parse. 
\end{itemize}

Overall, this proposal is aimed at making it easier for network appliances such
as HTTP reverse-proxies to inspect and route incoming HTTP traffic.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{SPDY}
\label{sec:intro/spdy}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The most interesting and likely to succeed proposal, SPDY is rather mature
at this point in time, having been implemented in both the most recent Chrome
and Firefox browsers in addition to modules and patches to make Apache and Nginx
webservers speak SPDY.  This protocol springs from a rather unique event in the
history of the web. Google is positioned such that they control a large portion
of both the browser and website markets simultaneously. This has allowed them to
define their own protocol without going through the notoriously slow IETF
process.  The most important parts of SPDY as of draft 3 (most recent complete version
 \cite{spdy3}) are framing and streams. 
\begin{description}
\item[Framing Layer] This binary protocol provides a layer on top of a reliable transport
protocol (recommended to be TCP) and provides a way for HTTP request/response
pairs to be issued and received out of order over a single transport layer
connection.  This provides an expected performance improvement of HTTP/1.1 by
not requiring multiple connections to the host to be made in order to
parallelize resource acquisition. There are 2 types of frames, first is control
frames which are responsible for managing the lifecycle of a stream, which we
will define soon.  Next is the data frame which is used simply to transmit data
also allowing for streaming. 
\item[Streaming] Streams are bidirectional and are used to send out of order
responses to requests. Importantly, streams can have priorities set by the
creator of the stream.  This, in conjunction with server-push (defined next)
allows for more important assets to be sent over the wires first.  An example of
the usefulness of this feature is a webpage with many images that are
unimportant for the actual content and layout of the page.  In that case, the
images could be given a low priority and sent last.
\item[Server-Push] Once a server receives a request for an asset, if it is aware
of closely connected assets, it may send them behind the original response,
without waiting for the client to request them.  This will pre-populate the
cache of the client and save a round trip time for each item.
\item[Header Compression with Dictionary] If there are many small assets on a
webpage, then a significant portion of the transmitted bytes will be due to HTTP
headers rather than the actual content.  If this can be compressed, much
bandwidth is saved~\cite{binoy}.
\end{description}

Together these make for a promising platform for the next version of HTTP.  As
stated earlier, this is the most likely starting point for the new protocol. It
is important to note that currently SPDY requires SSL/TLS to upgrade the
connection and it is likely that in the future SSL/TLS will be explicitly
required.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Speed+Mobility}
\label{sec:intro/s+m}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This proposal~\cite{sm} comes from Microsoft.  It shares much in common with SPDY, but
with a few major differences. First is that rather than defining their own
session layer, Microsoft S+M relies on WebSockets for a session layer.  In
addition (this is very important), S+M uses HTTP to negotiate the protocol
upgrade rather than SPDY's use of SSL/TLS to do this same thing. This adds quite
a bit of latency to beginning the actual communication and is one of the reasons that
Facebook endorsed SPDY~\cite{fbook}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiment}
\label{sec:project}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The experiment uses a client-server architecture to gather data about the
effectiveness of the SPDY protocol. The server can be run from any standard
machine, but only a single one will be run for the experiment.  The client is
the real measurement platform and will be distributed to volunteers to run in
order to test SPDY in a number of different network conditions.  The client will
collect data and report back to the server anonymous information about how
performant the protocol was in addition to helpful details that may help break
down what caused variations in results.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Collector}
\label{sec:project/collector}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The server described in \S\ref{sec:project/server} needs to correctly simulate
real world webpages. In order to facilitate this, websites from the Alexa
rankings\footnote{\url{http://www.alexa.com}} have been scraped and the size and
number of assets on each recorded.  This database will be accessed by the server
upon each request in order to determine which data to return.  Great
consideration was taken to make sure that this data accurately represents the
state of the web, including executing javascript from each page in a headless
browser in order to find dynamically loaded assets\footnote{Thanks to Tom Dooner
for doing much implementation of this part of the collecting}. This is not part
of the proposed project as the work has already been completed in conjunction
with another student.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Server}
\label{sec:project/server}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
If each client accessed all of the websites we scraped, the process would take
an insufferably long time.  Therefore, we have decided on the following
breakdown
\begin{center}
\begin{tabular}{ccc}
$1-100$ top sites & 10\% of $100-1000$ sites & 1\% of $1000-10000$ sites \\
\end{tabular}
\end{center}

These sites will be selected randomly and made into a list for the client to
consume. This is a total of 280 sites that run the gamut from representing the
largest and most frequented sites on the web, down to some of the most obscure.

The client can access the server using standard RESTful paths in two fashions
\begin{itemize}
\item \texttt{/site/<n>} where \texttt{n} is an integer that specifies the index
of the website simulation that is being accessed.  This will result in the
server returning fully formed HTML containing assets that map to the proper size
of the assets from the scraped page.  The rest of the document will be filled
with random bytes until it is the proper size of the recorded webpage that was
scraped.
\item \texttt{/img/<m>} where \texttt{m} is an integer specifying the size of the
asset that should be downloaded. So, in the case that we found a 2 MB image on a
webpage that is being simulated, \texttt{m} will be 2,000,000 and the server
will return a binary blob of that size. It is possible that this could take into
account the different compressibility of text to images.  For instance, an asset
that was javascript should have somewhat less random data supplied so that it
may compress more readily as compared to an image which doesn't compress very
much on top of its generally pre-compressed format.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Client}
\label{sec:project/client}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The client should be cross platform and easy to run.  The ultimate goal is for
it to be as simple as downloading and clicking on an executable of some form.
The client will access each of the tests specified in the list in turn using
both SPDY and HTTP/1.1 with SSL/TLS and
record timing information about how long it takes for each request to complete.
After this step is complete, the client will gather data about its location and
other considerations in order to return to the server for analysis.  All data
returned will be presented to the user to approve \textbf{before} being sent back.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Evaluation}
\label{sec:eval}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Once this data is collected the time difference will be found between each
protocol's retrieval of each test page. The obvious next step will be to
determine if SPDY actually made the pages load faster or not. In all likelihood,
there will not be a constant speedup across all pages and so the next step of
evaluation will be to see in which cases an improvement was found. This should
give insight into how SPDY improves over the prior specification and help decide
whether or not it is worth it for the actual upgrade of HTTP to take place.

This success of this experiment will be based off of how many points of data can
be acquired and how varying the conditions are for them.  Much of what will be
included in the final report will be plots and tables of the data collected to
allow the reader to decide for themselves.  This information will be useful to
others and the measurement platform itself should be designed in such a way that
future experiments can be run on it without too much effort to retool it.

\bibliographystyle{plain}
\bibliography{rfc,citations}

\end{document}

### 2012-11-30 spdyathome/client.py
Clean up stops and runs and add ip and identifier

@@ -7,6 +7,7 @@ import argparse
 import random
 import datetime
 import sys
+import socket
 from . import conf
 from thor import HttpClient
 from thor import SpdyClient
@@ -20,7 +21,7 @@ def get_args():
 
 
 def hello(host):
-    resp = {'text': '', 'sitelist': []}
+    resp = {'text': '', 'sitelist': [], 'ip': ''}
 
     def hello_start(status, phrase, headers):
         if status == '200':
@@ -30,7 +31,9 @@ def hello(host):
         resp['text'] += chunk
 
     def hello_stop(trailers):
-        resp['sitelist'] = json.loads(resp['text'])
+        dct = json.loads(resp['text'])
+        resp['sitelist'] = dct['sitelist']
+        resp['ip'] = dct['ip']
         stop()
 
     def hello_err(err):
@@ -49,7 +52,7 @@ def hello(host):
     hello.request_start('GET', uri, [])
     hello.request_done([])
     run()
-    return resp['sitelist']
+    return resp
 
 
 def collect(host, data):
@@ -87,7 +90,6 @@ def http_siteget(http1, http2, site):
         resp['text'] += chunk
 
     def site_stop(trailers):
-        print 'HTTP:',
         assetlist = json.loads(resp['text'])['list']
         for asset in assetlist:
             http_assetget(http1, http2, asset, httpclient)
@@ -95,6 +97,7 @@ def http_siteget(http1, http2, site):
         stop()
 
     t0 = time.time()
+    print 'HTTP:',
     httpclient = HttpClient()
     get = httpclient.exchange()
     get.on('response_start', site_start)
@@ -149,13 +152,13 @@ def spdy_siteget(spdy1, spdy2, site):
 
     def site_stop(trailers):
         assetlist = json.loads(resp['text'])['list']
-        print 'SPDY:',
         for asset in assetlist:
             spdy_assetget(spdy1, spdy2, asset, spdyclient)
         print
         stop()
 
     t0 = time.time()
+    print 'SPDY:',
     spdyclient = SpdyClient()
     get = spdyclient.exchange()
     uri = spdy1 + '/site/' + str(site)
@@ -205,35 +208,54 @@ def main():
     secondhost_spdy = conf.secondhost + ':' + str(conf.spdy_port)
     mainhost_collect = conf.mainhost + ':' + str(conf.capture_port)
 
-    times = {}
-    sites = hello(mainhost_http)
[…]

### 2012-11-30 spdyathome/serverbase.py

@@ -34,7 +34,8 @@ class BaseServer(object):
     def gethello(self, res):
         headers = []
         res.response_start(200, 'OK', headers)
-        res.response_body(json.dumps(self.sitelist))
+        ip = res.http_conn.tcp_conn.socket.getpeername()[0]
+        res.response_body(json.dumps({'sitelist': self.sitelist, 'ip': ip}))
         res.response_done([])
 
     """

### 2012-12-01 paper/paper.tex
Shuffle around some sections in the paper
Also write a bit more

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+\section{Background}
 \label{sec:intro}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The most recent httbis working group charter includes the following
-goals~\cite{httpbis-charter}:
+HTTP is one of the most widely used application-level protocols. Initially
+written in 1996~\cite{http1rfc}, HTTP was written for a different era of web
+sites -- before streaming video websites, before asset-heavy web pages, and
+before mostly-Javascript web applications like Google's Gmail, Twitter, and
+Facebook.
+
+Although HTTP was amended in 1999 to include better support for caching, the
+ability to reuse connections, and other helpful features, the World Wide Web
+landscape has changed significantly since then -- led by big technology
+companies desiring to optimize application speed and user experience.
+
+The IETF's httpbis working group is responsible for maintaining and developing
+the HTTP specification, including all aspects pertaining to developing a new
+HTTP specification, HTTP/2.0. The most recent httpbis working group charter
+mentions the following goals for HTTP/2.0~\cite{httpbis-charter}:
 \begin{itemize}
@@
 \end{itemize}
-The current self-imposed deadline for the spec is July
-2013~\cite{httpbis-charter}.  There are currently 3 likely starting points for
-the specification that have been proposed. They will be covered beginning in
-\S\ref{sec:intro/opensource}. The most important part of the goals that is not
-explicitly mentioned is that these proposals must maintain semantic equivalence
-with the currently implemented HTTP specification; changes may only be made to
-the method in which these request/response pairs are transmitted.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Problem Statement}
-\label{sec:intro/problem}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The web has developed to the point where HTTP/1.1 is no longer sufficient to
-architect our major web applications. The basic semantic meaning is excellent,
-and is the foundation of the web, but certain engineering considerations must be
-taken into account in order to improve the protocol.  One proposal for this next
-generation protocol is Google's SPDY~\cite{spdyspec}.  Most agree that this protocol will
-be optimal for Google, but the question remains whether or not this will be an
-improvement for the vast majority of the web.  Does the rather drastic increase
-in complexity pay off in the general case, and is it worth the added cost in
-terms of development time to support this protocol everywhere?
+The most important part of the goals that is not explicitly mentioned is that
+these proposals must maintain semantic equivalence with the currently
+implemented HTTP specification; changes may only be made to the method in
+which these request/response pairs are transmitted.
 
-This project sets out to answer that question in two fashions.  First with an in
-depth examination of what is the limiting factor of current HTTP/1.1 including a
-review of literature in the area.  More importantly, an experiment will be
-conducted to determine empirically how much of an improvement is seen when using
-SPDY rather than HTTP.  The experiment is proposed in \S\ref{sec:project}. The
-remainder of this section will give a quick overview of the proposals to replace
-HTTP/1.1.
+The current self-imposed deadline for HTTP/2.0 is July
+2013~\cite{httpbis-charter}.  So far, three likely starting points for
+the specification have been proposed: Google's SPDY, Microsoft's Speed +
+Mobility, and a "Network-Friendly" proposal from a handful of Open Source
+authors. The three will be briefly outlined beginning in
+\S\ref{sec:intro/spdy} and then the remainder of the paper will focus on
+measurements of the most viable candidate for HTTP/2.0, SPDY.
 
 % TODO: Expand on these for the full paper!
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Network-Friendly}
-\label{sec:intro/opensource}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-This proposal comes from a group of open-source developers without any strict
-ties to a company or organization otherwise.  It is quite different from the
-other two proposals because it is looking at the problem from another angle.
-The four main ideas in this proposal are~\cite{friendly}
-\begin{itemize}
-\item Binary encoding of header fields\footnote{This might be expected
-considering that one of the primary authors of this proposal is the creator of
-the Varnish Cache \url{https://www.varnish-cache.org/} which must inspect the
-header fields of incoming requests.}
-\item Grouping of common header fields allowing for reduced header size when
-repeated requests are made.
-\item Multiplexing of request and response.  This is something shared in common
-with all three of the currently viable proposals.
-\item A layering model that is easier for intermediaries like Varnish to parse. 
-\end{itemize}
-
-Overall, this proposal is aimed at making it easier for network appliances such
-as HTTP reverse-proxies to inspect and route incoming HTTP traffic.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 at this point in time, having been implemented in both the most recent Chrome
-and Firefox browsers in addition to modules and patches to make Apache and Nginx
-webservers speak SPDY.  This protocol springs from a rather unique event in the
-history of the web. Google is positioned such that they control a large portion
-of both the browser and website markets simultaneously. This has allowed them to
-define their own protocol without going through the notoriously slow IETF
-process.  The most important parts of SPDY as of draft 3 (most recent complete version
+and Firefox browsers in addition to having modules and patches for both the
+Apache and Nginx web servers which allow them to speak SPDY.
+
+This protocol springs from a rather unique event in the history of the web.
+Google is positioned such that they control a large portion of both the browser
+and website markets simultaneously. This has allowed them to define their own
+protocol without going through the traditionally slow IETF process. This is
+notable because it gives empiricists the ability to measure real-world
+performance metrics whilst implementing websites may benefit from the new
+protocol in the short term.
+
+The most important parts of SPDY as of draft 3 (most recent complete version
 \cite{spdy3}) are framing and streams.
+
 \begin{description}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Speed+Mobility}
+\label{sec:intro/s+m}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+This proposal~\cite{sm} comes from Microsoft.  It shares much in common with
+SPDY, but with a few major differences. First is that rather than defining
+their own session layer, Microsoft S+M relies on WebSockets for a session
+layer.  In addition (this is very important), S+M uses HTTP to negotiate the
+protocol upgrade rather than SPDY's use of SSL/TLS to do this same thing. This
+adds quite a bit of latency to beginning the actual communication and is one of
+the reasons that Facebook endorsed SPDY~\cite{fbook}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Network-Friendly}
+\label{sec:intro/opensource}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+This proposal comes from a group of open-source developers without any strict
+ties to a company or organization otherwise.  It is quite different from the
+other two proposals because it is looking at the problem from another angle.
+The four main ideas in this proposal are~\cite{friendly}
+\begin{itemize}
+\item Binary encoding of header fields\footnote{This might be expected
+considering that one of the primary authors of this proposal is the creator of
+the Varnish Cache \url{https://www.varnish-cache.org/} which must inspect the
+header fields of incoming requests.}
+\item Grouping of common header fields allowing for reduced header size when
+repeated requests are made.
+\item Multiplexing of request and response.  This is something shared in common
+with all three of the currently viable proposals.
+\item A layering model that is easier for intermediaries like Varnish to parse.
+\end{itemize}
+
+Overall, this proposal is aimed at making it easier for network appliances such
+as HTTP reverse-proxies to inspect and route incoming HTTP traffic.
+
 Together these make for a promising platform for the next version of HTTP.  As
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Speed+Mobility}
-\label{sec:intro/s+m}
+\section{Experiments}
+\label{sec:project}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-This proposal~\cite{sm} comes from Microsoft.  It shares much in common with SPDY, but
-with a few major differences. First is that rather than defining their own
-session layer, Microsoft S+M relies on WebSockets for a session layer.  In
-addition (this is very important), S+M uses HTTP to negotiate the protocol
-upgrade rather than SPDY's use of SSL/TLS to do this same thing. This adds quite
-a bit of latency to beginning the actual communication and is one of the reasons that
-Facebook endorsed SPDY~\cite{fbook}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Experiment}
-\label{sec:project}
+\subsection{Problem Statement}
+\label{sec:project/problem}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The web has developed to the point where HTTP/1.1 is no longer sufficient to
+architect our major web applications. The basic semantic meaning is excellent,
+and is the foundation of the web, but certain engineering considerations must
+be taken into account in order to improve the protocol. For example, Google has
+made heavy investments in SPDY, but the question remains whether or not this
+will be an improvement for the vast majority of the web.  Does the rather
+drastic increase in complexity pay off in the general case, and is it worth the
+added cost in terms of development time to support this protocol everywhere?
+
+This project sets out to answer that question in two fashions.  First with an
+in-depth examination of what is the limiting factor of current HTTP/1.1
+including a review of literature in the area and a characterization of
+real-world web page asset size distribution (and how we predict the same assets
+will load if loaded over SPDY).  Then, we will collect direct measurements with
+a simulated browser experiment to determine empirically how much of an
+improvement is seen when using SPDY rather than HTTP.  The experiment is
+proposed in \S\ref{sec:project}.
+
 The experiment uses a client-server architecture to gather data about the
 effectiveness of the SPDY protocol. The server can be run from any standard
-machine, but only a single one will be run for the experiment.  The client is
-the real measurement platform and will be distributed to volunteers to run in
-order to test SPDY in a number of different network conditions.  The client will
-collect data and report back to the server anonymous information about how
-performant the protocol was in addition to helpful details that may help break
-down what caused variations in results.
+machine, but only a single one will be run for the experiment.  The client (the
+``collector'') is the real measurement platform and will be distributed to
+volunteers to run in order to test SPDY in a number of different network
+conditions.  The client will collect data and report back to the server
+anonymous information about how performant the protocol was in addition to
+helpful details that may help break down what caused variations in results.
 
+%%%%%%%%%%%%%%%%%
+%% Tom has read through here ^^^^^^
+%%    12/1/2012
+%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2012-12-02 spdyathome/servers.py
Update sitelist to be not rediculous

@@ -4,6 +4,7 @@ Use the standard request responders in BaseServer.
 """
 import urilib
 import os
+import sys
 import argparse
 from . import conf
 from . import util
@@ -102,6 +103,7 @@ def capture_main(conf):
 
 if __name__ == '__main__':
     args = get_args()
+    sys.setrecursionlimit(2000)  # I'm so sorry...
 
     try:
         os.mkdir(conf.outdir)

### 2012-12-03 analysis/basic.py
Add analysis code

@@ -1,0 +1,22 @@
+#!/usr/bin/python
+"""
+Find which protocol was faster for each of the 2** sites.
+"""
+import sys
+import json
+
+if __name__ == '__main__':
+    f = open(sys.argv[1])
+    for line in f:
+        blob = json.loads(line)
+        count = 0
+        good = 0
+        for site,vals in blob.items():
+            if type(vals) != dict:
+                continue
+            spdy = float(vals['spdy']['time'])
+            http = float(vals['http']['time'])
+            count += 1
+            if spdy < http:
+                good += 1
+        print '%f/%f' % (good, count)

### 2012-12-10 analysis/count_responders.py
Add count_responders script

@@ -1,0 +1,17 @@
+#!/usr/bin/python
+"""
+Find which protocol was faster for each of the 2** sites.
+"""
+import sys
+import json
+
+if __name__ == '__main__':
+    f = open(sys.argv[1])
+    ips = set()
+    uniqs = set()
+    for line in f:
+        blob = json.loads(line)
+        ips.add(blob['ip'])
+        uniqs.add(blob['uniq'])
+    print 'ips:', len(ips)
+    print 'ids:', len(uniqs)

### 2012-12-10 paper/paper.tex
Add me to authors

@@
 \author{Brian Stack\thanks{ bis12@case.edu, Case Western Reserve University,
-Cleveland, OH 44106}}
+Cleveland, OH 44106}, Tom Dooner\thanks{ ted27@case.edu }}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Background}
-\label{sec:intro}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\label{sec:background}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 HTTP is one of the most widely used application-level protocols. Initially
@@
 authors. The three will be briefly outlined beginning in
-\S\ref{sec:intro/spdy} and then the remainder of the paper will focus on
+\S\ref{sec:background/spdy} and then the remainder of the paper will focus on
 measurements of the most viable candidate for HTTP/2.0, SPDY.
@@
 \subsection{SPDY}
-\label{sec:intro/spdy}
+\label{sec:background/spdy}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Speed+Mobility}
-\label{sec:intro/s+m}
+\label{sec:background/s+m}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Network-Friendly}
-\label{sec:intro/opensource}
+\label{sec:background/opensource}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Experiments}
-\label{sec:project}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Problem Statement}
-\label{sec:project/problem}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Research Areas}
+\label{sec:research}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 The web has developed to the point where HTTP/1.1 is no longer sufficient to
@@
 
-This project sets out to answer that question in two fashions.  First with an
-in-depth examination of what is the limiting factor of current HTTP/1.1
-including a review of literature in the area and a characterization of
-real-world web page asset size distribution (and how we predict the same assets
-will load if loaded over SPDY).  Then, we will collect direct measurements with
-a simulated browser experiment to determine empirically how much of an
-improvement is seen when using SPDY rather than HTTP.  The experiment is
-proposed in \S\ref{sec:project}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Overview}
+\label{sec:research/overview}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+This project sets out to answer that question in two fashions. First, we will
+perform an in-depth examination of what is the limiting factor of current
+HTTP/1.1 including a review of literature in the area and a characterization of
+real-world web page asset size distribution in \S\ref{sec:assets} (and
+how we predict the same assets will load if loaded over SPDY). Since SPDY can
+combine asset requests into a single multiplexed TCP connection, we identify
+this as a significant source of performance improvement over HTTP. We will
+perform this by collecting the assets from the top Alexa sites with the Web
+Asset Scraper described in \S\ref{sec:research/scraper}.
 
-The experiment uses a client-server architecture to gather data about the
-effectiveness of the SPDY protocol. The server can be run from any standard
-machine, but only a single one will be run for the experiment.  The client (the
-``collector'') is the real measurement platform and will be distributed to
-volunteers to run in order to test SPDY in a number of different network
-conditions.  The client will collect data and report back to the server
-anonymous information about how performant the protocol was in addition to
-helpful details that may help break down what caused variations in results.
+But how will \textit{real} web sites perform when their assets are multiplexed?
+Since only a handful of (already optimized) sites implement SPDY, we must
+collect direct measurements with a simulated browser. The simulated
+client/server will experimentally determine empirically how much of an
+improvement is seen when using SPDY rather than HTTP.  The simulation is
+proposed in \S\ref{sec:research/client-server}.
 
-%%%%%%%%%%%%%%%%%
-%% Tom has read through here ^^^^^^
-%%    12/1/2012
-%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Collector}
-\label{sec:project/collector}
+\subsection{Web Asset Scraper}
+\label{sec:research/scraper}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Server}
-\label{sec:project/server}
+\subsection{Client/Server Implementation}
+\label{sec:research/client-server}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The simulation uses a client-server architecture to gather data about the
+effectiveness of the SPDY protocol. The server can be run from any standard
+machine, but only a single one will be run for the experiment.  The client (the
+``collector'') is the real measurement platform and will be distributed to
+volunteers to run in order to test SPDY in a number of different network
+conditions.  The client will collect data and report back to the server
+anonymous information about how performant the protocol was in addition to
+helpful details that may help break down what caused variations in results.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Server}
+\label{sec:research/server}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 If each client accessed all of the websites we scraped, the process would take
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Client}
-\label{sec:project/client}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Client}
+\label{sec:research/client}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 The client should be cross platform and easy to run.  The ultimate goal is for
@@
 other considerations in order to return to the server for analysis.  All data
-returned will be presented to the user to approve \textbf{before} being sent back.
+returned will be presented to the user to approve \textbf{before} being sent
+back.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Evaluation}
-\label{sec:eval}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Once this data is collected the time difference will be found between each
-protocol's retrieval of each test page. The obvious next step will be to
-determine if SPDY actually made the pages load faster or not. In all likelihood,
-there will not be a constant speedup across all pages and so the next step of
-evaluation will be to see in which cases an improvement was found. This should
-give insight into how SPDY improves over the prior specification and help decide
-whether or not it is worth it for the actual upgrade of HTTP to take place.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Asset Characterization}
+\label{sec:assets}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+here is where we will discuss the asset measurement stuff.
 
-This success of this experiment will be based off of how many points of data can
-be acquired and how varying the conditions are for them.  Much of what will be
-included in the final report will be plots and tables of the data collected to
-allow the reader to decide for themselves.  This information will be useful to
-others and the measurement platform itself should be designed in such a way that
-future experiments can be run on it without too much effort to retool it.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Real World SPDY vs. HTTP}
+\label{sec:realworld}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+here is where we will discuss brian's spdyathome results
+
+% I don't want to remove this wholesale but I don't think it is relevant
+% anywhere else in the paper. Maybe it fits somewhere?
+% -Tom
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \section{Evaluation}
+% \label{sec:eval}
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Once this data is collected the time difference will be found between each
+% protocol's retrieval of each test page. The obvious next step will be to
+% determine if SPDY actually made the pages load faster or not. In all likelihood,
+% there will not be a constant speedup across all pages and so the next step of
+% evaluation will be to see in which cases an improvement was found. This should
+% give insight into how SPDY improves over the prior specification and help decide
+% whether or not it is worth it for the actual upgrade of HTTP to take place.
+%
+% This success of this experiment will be based off of how many points of data can
+% be acquired and how varying the conditions are for them.  Much of what will be
+% included in the final report will be plots and tables of the data collected to
+% allow the reader to decide for themselves.  This information will be useful to
+% others and the measurement platform itself should be designed in such a way that
+% future experiments can be run on it without too much effort to retool it.
 

### 2012-12-11 analysis/plot1.py
Add first 3 plots

@@ -1,0 +1,22 @@
+#!/usr/bin/python
+"""
+1. plot of difference between speeds
+"""
+import sys
+import json
+
+if __name__ == '__main__':
+    f = open(sys.argv[1])
+    speed_diffs = []
+    for line in f:
+        blob = json.loads(line)
+        count = 0
+        good = 0
+        for site,vals in blob.items():
+            if type(vals) != dict:
+                continue
+            spdy = float(vals['spdy']['time'])
+            http = float(vals['http']['time'])
+            speed_diffs.append(http - spdy)
+    for x in sorted(speed_diffs):
+        print x

### 2012-12-11 analysis/plot3.py

@@ -1,0 +1,22 @@
+#!/usr/bin/python
+"""
+3. average over the course of a whole responder  otherwise same as plot1
+"""
+import sys
+import json
+
+if __name__ == '__main__':
+    f = open(sys.argv[1])
+    speed_diffs = []
+    for line in f:
+        sd = []
+        blob = json.loads(line)
+        for site,vals in blob.items():
+            if type(vals) != dict:
+                continue
+            spdy = float(vals['spdy']['time'])
+            http = float(vals['http']['time'])
+            sd.append(http - spdy)
+        speed_diffs.append(sum(sd)/len(sd))
+    for x in sorted(speed_diffs):
+        print x

### 2012-12-11 analysis/plot9.py

@@ -1,0 +1,24 @@
+#!/usr/bin/python
+"""
+9. same as plot1 except average across site
+"""
+import sys
+import json
+
+if __name__ == '__main__':
+    f = open(sys.argv[1])
+    speed_diffs = {}
+    for line in f:
+        blob = json.loads(line)
+        for site,vals in blob.items():
+            if type(vals) != dict:
+                continue
+            spdy = float(vals['spdy']['time'])
+            http = float(vals['http']['time'])
+            if site in speed_diffs:
+                speed_diffs[site].append(http - spdy)
+            else:
+                speed_diffs[site] = [http - spdy]
+    avgs = [sum(x)/len(x) for x in speed_diffs.values()]
+    for x in sorted(avgs):
+        print x

### 2012-12-11 analysis/basic.py
Add plot2 and fix mistake in analysis

@@ -16,6 +16,8 @@ if __name__ == '__main__':
                 continue
             spdy = float(vals['spdy']['time'])
             http = float(vals['http']['time'])
+            if spdy == -1 or http == -1:
+                continue
             count += 1
             if spdy < http:
                 good += 1

### 2012-12-11 analysis/plot2.py

@@ -1,17 +1,14 @@
 #!/usr/bin/python
 """
-1. plot of difference between speeds
+2. scatter of speed difference vs total time taken
 """
 import sys
 import json
 
 if __name__ == '__main__':
     f = open(sys.argv[1])
-    speed_diffs = []
     for line in f:
         blob = json.loads(line)
-        count = 0
-        good = 0
         for site,vals in blob.items():
             if type(vals) != dict:
                 continue
@@ -19,6 +16,5 @@ if __name__ == '__main__':
             http = float(vals['http']['time'])
             if spdy == -1 or http == -1:
                 continue
-            speed_diffs.append(http - spdy)
-    for x in sorted(speed_diffs):
-        print x
+            # Print avg of time to download, difference in speed pairs
+            print (http + spdy)/2, http - spdy

### 2012-12-11 analysis/plot3.py

@@ -16,6 +16,8 @@ if __name__ == '__main__':
                 continue
             spdy = float(vals['spdy']['time'])
             http = float(vals['http']['time'])
+            if spdy == -1 or http == -1:
+                continue
             sd.append(http - spdy)
         speed_diffs.append(sum(sd)/len(sd))
     for x in sorted(speed_diffs):

### 2012-12-11 analysis/plot9.py

@@ -15,6 +15,8 @@ if __name__ == '__main__':
                 continue
             spdy = float(vals['spdy']['time'])
             http = float(vals['http']['time'])
+            if spdy == -1 or http == -1:
+                continue
             if site in speed_diffs:
                 speed_diffs[site].append(http - spdy)
             else:

### 2012-12-11 analysis/plot5.py
Add plot5

@@ -1,0 +1,37 @@
+#!/usr/bin/python
+"""
+5. whisker plot for any multiple responders
+"""
+import sys
+import json
+
+if __name__ == '__main__':
+    f = open(sys.argv[1])
+    responders = {}
+    for line in f:
+        sd = []
+        blob = json.loads(line)
+        for site,vals in blob.items():
+            if type(vals) != dict:
+                continue
+            spdy = float(vals['spdy']['time'])
+            http = float(vals['http']['time'])
+            if spdy == -1 or http == -1:
+                continue
+            sd.append(http - spdy)
+        if blob['ip'] in responders:
+            responders[blob['ip']].append(sum(sd)/len(sd))
+        else:
+            responders[blob['ip']] = [sum(sd)/len(sd)]
+
+    i = 1
+    for x in responders.values():
+        if len(x) < 5:
+            continue
+        print i,
+        print min(x),
+        print x[int(len(x)/4)],
+        print sum(x)/len(x),
+        print x[3*int(len(x)/4)],
+        print max(x)
+        i += 1

### 2012-12-11 analysis/geoip.rb
Add geoip reporting

@@ -1,0 +1,17 @@
+require 'geoip'
+require 'json'
+
+c = GeoIP.new('GeoLiteCity.dat')
+h = Hash.new(0)
+
+File.open(ARGV[0]).each_line do |l|
+    blob = JSON.parse(l)
+    h[c.city(blob['ip']).city_name] += 1
+end
+
+h.sort_by{|k,v| -v}.each do |k,v|
+    if k == ''
+        k = 'unknown'
+    end
+    puts "#{k}: #{v}"
+end

### 2012-12-11 analysis/plot6.py
Add plot6

@@ -1,0 +1,24 @@
+#!/usr/bin/python
+"""
+1. plot of difference between speeds
+"""
+import sys
+import json
+
+if __name__ == '__main__':
+    f = open(sys.argv[1])
+    speed_diffs = []
+    for line in f:
+        blob = json.loads(line)
+        count = 0
+        good = 0
+        for site,vals in blob.items():
+            if type(vals) != dict:
+                continue
+            spdy = float(vals['spdy']['time'])
+            http = float(vals['http']['time'])
+            if spdy == -1 or http == -1:
+                continue
+            speed_diffs.append(http - spdy)
+    for x in speed_diffs:
+        print x

### 2012-12-11 analysis/plot12.py
Add plot12

@@ -1,0 +1,24 @@
+#!/usr/bin/python
+"""
+2. scatter of speed difference vs total time taken
+"""
+import sys
+import json
+
+if __name__ == '__main__':
+    f = open(sys.argv[1])
+    for line in f:
+        blob = json.loads(line)
+        sd = []
+        avgs = []
+        for site,vals in blob.items():
+            if type(vals) != dict:
+                continue
+            spdy = float(vals['spdy']['time'])
+            http = float(vals['http']['time'])
+            if spdy == -1 or http == -1:
+                continue
+            sd.append(http - spdy)
+            avgs.append((http + spdy)/2)
+        # Print avg of time to download, difference in speed pairs
+        print sum(avgs)/len(avgs), sum(sd)/len(sd)

### 2012-12-11 analysis/plot13.py
plot13

@@ -1,0 +1,27 @@
+#!/usr/bin/python
+"""
+5. whisker plot for any multiple responders
+"""
+import sys
+import json
+
+if __name__ == '__main__':
+    f = open(sys.argv[1])
+    sites = {}
+    for line in f:
+        blob = json.loads(line)
+        for site,vals in blob.items():
+            if type(vals) != dict:
+                continue
+            spdy = float(vals['spdy']['time'])
+            http = float(vals['http']['time'])
+            if spdy == -1 or http == -1:
+                continue
+            if site in sites:
+                sites[site].append(http - spdy)
+            else:
+                sites[site] = [http - spdy]
+
+    s_sites = [sum(x)/len(x) for x in sites.values()]
+    for time in sorted(s_sites):
+        print time

### 2012-12-11 analysis/plot8.py

@@ -1,0 +1,20 @@
+#!/usr/bin/python
+"""
+8. scatter of speedup vs site size
+"""
+import sys
+import json
+
+if __name__ == '__main__':
+    f = open(sys.argv[1])
+    for line in f:
+        blob = json.loads(line)
+        for site,vals in blob.items():
+            if type(vals) != dict:
+                continue
+            spdy = float(vals['spdy']['time'])
+            http = float(vals['http']['time'])
+            if spdy == -1 or http == -1:
+                continue
+            # Print avg of time to download, difference in speed pairs
+            print (http + spdy)/2, http - spdy

### 2012-12-11 analysis/plot10.py
Add plot8 and plot10

@@ -1,6 +1,6 @@
 #!/usr/bin/python
 """
-8. scatter of speedup vs site size
+10. scatter of speedup vs asset count
 """
 import sys
 import json
@@ -34,7 +34,4 @@ if __name__ == '__main__':
             if spdy == -1 or http == -1:
                 continue
             # Print avg of time to download, difference in speed pairs
-            size = 0
-            for asset in sites[site]['assets'].values():
-                size += int(asset['size'])
-            print size, http - spdy
+            print len(sites[site]['assets']), http - spdy

### 2012-12-16 paper/paper.tex
Add some more about the Web Asset Scraper
And some other stuff got lumped in here as well. Good.

@@
 
-\title{An Investigation of the SPDY Protocol}
+\title{An Analysis of the SPDY Protocol as a Candidate for HTTP/2.0}
 \date{\today}
@@
 creator of the stream.  This, in conjunction with server-push (defined next)
-allows for more important assets to be sent over the wires first.  An example of
-the usefulness of this feature is a webpage with many images that are
-unimportant for the actual content and layout of the page.  In that case, the
-images could be given a low priority and sent last.
+allows for more important assets (images, javascripts, stylesheets, etc.) to be
+sent over the wires first.  An example of the usefulness of this feature is a
+webpage with many images that are unimportant for the actual content and layout
+of the page.  In that case, the images could be given a low priority and sent
+last.
 \item[Server-Push] Once a server receives a request for an asset, if it is aware
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The server described in \S\ref{sec:project/server} needs to correctly simulate
-real world webpages. In order to facilitate this, websites from the Alexa
-rankings\footnote{\url{http://www.alexa.com}} have been scraped and the size and
-number of assets on each recorded.  This database will be accessed by the server
-upon each request in order to determine which data to return.  Great
-consideration was taken to make sure that this data accurately represents the
-state of the web, including executing javascript from each page in a headless
-browser in order to find dynamically loaded assets\footnote{Thanks to Tom Dooner
-for doing much implementation of this part of the collecting}. This is not part
-of the proposed project as the work has already been completed in conjunction
-with another student.
+The server described in \S\ref{sec:research/server} needs to correctly simulate
+real world webpages. In order to achieve this, we created a web scraping tool
+which scraped websites chosen from the Alexa most popular websites
+list\footnote{\url{http://www.alexa.com}} and recorded the size and number of
+assets into a database.  This database will be accessed by the server upon each
+request in order to determine which data to return.  In order to accurately
+represent the original websites (and the state of the web), we employed a
+headless web browser PhantomJS\footnote{\url{http://phantomjs.org}} which
+mimicked a user's browser and thus requested all assets needed to render a web
+page, even the dynamically loaded ones buried in CSS rules or Javascript.
+
+We desire to record information that will allow us to assess the performance
+characteristics of SPDY for each website we scrape. We recorded, for each
+asset, the source IP we downloaded the asset from, the SSL certificate (if any)
+for the connection on which we downloaded the asset, and the asset's filename
+and filesize.
+
+Not every website supports SSL, and the Alexa list ranks websites by hostname
+combining SSL and non-SSL traffic. Since we are not measuring the time to
+download the asset, we can default to SSL for websites that support it, as we
+can determine useful information about the owner of assets from the SSL
+certificate. For sites that do not support SSL, we will request the non-SSL
+HTTP hostname.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-here is where we will discuss the asset measurement stuff.
+\subsection{SPDY Combination Strategy}
+SPDY's most complex new feature is the ability to multiplex requests for assets
+over a single TCP connection. In this way, a web page's assets can benefit from
+a warmed-up TCP connection which is not subject to the TCP slow start
+algorithm. Since SPDY is currently built atop SSL, SPDY can only combine assets
+with a mutually-agreeable SSL certificate.
+
+% we measure two approaches: splitting on SSL cert and IP and simply splitting
+% on SSL cert (as an upper bound for combination). The first method, ssl + ip,
+% is prone to some error due to the use of CDNs confusing our scraping of
+% assets.
 

### 2012-12-18 paper/paper.tex
Tom's work

@@
 algorithm. Since SPDY is currently built atop SSL, SPDY can only combine assets
-with a mutually-agreeable SSL certificate.
+with a mutually-agreeable SSL certificate. The assets will be combined into
+separate streams over the same TCP connection, thus ideally obtaining complete
+utilization of the connection and the benefit from TCP's eventual discovery of
+an accurate congestion window.
 
+In order to measure the efficiency of SPDY's asset combination, we must
+determine the benefit of combining assets. The authors of SPDY claim that the
+main benefit from asset combination is the reduction of network connections
+required~\cite{spdy-whitepaper}. Although the HTTP/1.1 specification allows for
+up to two simultaneous connections to servers, modern browsers willfully
+violate it in service of page load speed and will happily open up to six
+connections to each host. Websites have also been pushing the limits by
+creating semantically equivalent hostnames (i.e. assets1.example.com,
+assets2.example.com, etc.) for different asset servers so browsers will open
+six connections to each. Thus, browsers may wind up opening hundreds of
+connections immediately upon loading a page.
+
+SPDY's asset combination addresses this. In this section we will measure the
+difference in the number of connections required to load each page under two
+different assumptions: first that site owners could combine all assets with
+mutually-agreeable SSL certificates into one SPDY connection and second that
+site owners would combine all assets served by the same IP address \textit{and}
+with mutually-agreeable SSL certificates into one SPDY connection. Logically,
+the first method is an upper bound for the number of connections we can save,
+we estimate that the second method is more accurate for most websites but is a
+lower bound for websites which employ CDNs or asset host sharding.
+
+\subsection{SSL-only Asset Combination}
+\begin{figure}[h!]
+\includegraphics[width=0.4\textwidth,angle=270]{plots/asset_combination_only_ssl_ratio.eps}
+\caption{Connection Ratio -- SSL-only Combination Strategy}
+\label{fig:combination-ssl}
+\end{figure}
+The results in Figure \ref{fig:combination-ssl} assume that all assets
+described by a mutually-compatible SSL certificate are combined into one SPDY
+connection. Two assets have \textit{mutually-compatible} SSL certificates if
+their SSL certificates are valid for the host of the other asset (with either
+the Canonical Name or the Alternative Hostnames). In this way, we
+systematically combine assets by adding them to the largest group with which
+they are compatible. We then compare the number of asset groups (SPDY
+connections) with the number of assets (HTTP connections). The CDF of the ratio
+for the Alexa top 100,000 websites is plotted.
+
+\subsection{SSL-and-IP Asset Combination}
+\begin{figure}[h!]
+\includegraphics[width=0.4\textwidth,angle=270]{plots/asset_combination_ssl_and_ip_ratio.eps}
+\caption{Connection Ratio -- SSL-and-IP Combination Strategy}
+\label{fig:combination-ssl-and-ip}
+\end{figure}
+The results in Figure \ref{fig:combination-ssl-and-ip} assume that all assets
+described by a mutually-compatible SSL certificate and that are downloaded from
+the same IP in practice are combined into one SPDY connection.
+\subsection{Connection Sizes}
 % we measure two approaches: splitting on SSL cert and IP and simply splitting

### 2012-12-18 paper/paper.tex
Add another plot and some description of it

@@
 \begin{figure}[h!]
+\centering
 \includegraphics[width=0.4\textwidth,angle=270]{plots/asset_combination_only_ssl_ratio.eps}
@@
 \begin{figure}[h!]
+\centering
 \includegraphics[width=0.4\textwidth,angle=270]{plots/asset_combination_ssl_and_ip_ratio.eps}
@@
 the same IP in practice are combined into one SPDY connection.
+
 \subsection{Connection Sizes}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.4\textwidth]{plots/asset_combination_connection_sizes.eps}
+\caption{Connection Sizes After Asset Combination}
+\label{fig:connection-sizes}
+\end{figure}
+
+Figure \ref{fig:connection-sizes} describes the size of connections when all
+assets are combined together as described in the SSL-and-IP combination
+strategy. 70\% of SPDY connections are noticeably larger than HTTP connections,
+up to almost an order of magnitude in some cases. Some assets do not benefit
+from SPDY's combination: small assets like Google Analytics tracking
+Javascript, or external libraries used on web pages such as jQuery. These
+comprise the left part of the SPDY curve.
+
 % we measure two approaches: splitting on SSL cert and IP and simply splitting

### 2012-12-19 paper/paper.tex
More text...

@@
 
-% TODO: Expand on these for the full paper!
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+% TODO: Expand on these for the full paper!
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+As mentioned previously, this is an upper-bound for multiplexing savings.
+Results nonetheless are dramatic: about 90\% of sites could load using
+one-fifth the connections if combining assets via SPDY.
+
 \subsection{SSL-and-IP Asset Combination}
@@
 the same IP in practice are combined into one SPDY connection.
+
+Figure \ref{fig:combination-ssl-and-ip} shows that, in the common-to-worst
+case, 90\% of sites will halve the number of connections by switching to SPDY
+and 40\% could load using one-fifth the connections.
 

### 2012-12-19 paper/paper.tex
Rewrite some of the SPDY asset introduction

@@
 over a single TCP connection. In this way, a web page's assets can benefit from
-a warmed-up TCP connection which is not subject to the TCP slow start
+a warmed-up TCP connection which has passed the beginning of the TCP slow start
 algorithm. Since SPDY is currently built atop SSL, SPDY can only combine assets
 with a mutually-agreeable SSL certificate. The assets will be combined into
-separate streams over the same TCP connection, thus ideally obtaining complete
-utilization of the connection and the benefit from TCP's eventual discovery of
-an accurate congestion window.
+separate, interleaved streams over the same TCP connection, thus ideally
+obtaining complete utilization of the connection and the benefit from TCP's
+eventual discovery of an accurate congestion window.
 
 In order to measure the efficiency of SPDY's asset combination, we must
-determine the benefit of combining assets. The authors of SPDY claim that the
-main benefit from asset combination is the reduction of network connections
-required~\cite{spdy-whitepaper}. Although the HTTP/1.1 specification allows for
-up to two simultaneous connections to servers, modern browsers willfully
-violate it in service of page load speed and will happily open up to six
-connections to each host. Websites have also been pushing the limits by
-creating semantically equivalent hostnames (i.e. assets1.example.com,
-assets2.example.com, etc.) for different asset servers so browsers will open
-six connections to each. Thus, browsers may wind up opening hundreds of
-connections immediately upon loading a page.
+determine what metric benefits from combining assets. The authors of SPDY claim
+that the main benefit from asset combination is the reduction of network
+connections required~\cite{spdy-whitepaper}.
+
+Although the HTTP/1.1 specification allows for up to two simultaneous
+connections to servers, modern browsers willfully violate it in service of page
+load speed and will happily open up to six connections to each host. Websites
+have also been pushing the limits by creating semantically equivalent hostnames
+for asset servers (i.e. assets1.example.com, assets2.example.com, etc.) so
+browsers will open six connections to each. Thus, browsers may wind up opening
+hundreds of connections immediately upon loading a page -- thus dishonoring the
+intent of TCP slow start.
 

### 2012-12-19 paper/paper.tex
Add a bit more information to the S+M/Network Friendly

@@
 not requiring multiple connections to the host to be made in order to
-parallelize resource acquisition. There are 2 types of frames, first is control
-frames which are responsible for managing the lifecycle of a stream, which we
-will define soon.  Next is the data frame which is used simply to transmit data
-also allowing for streaming.
+parallelize resource acquisition. There are 2 types of frames: control
+frames and data frames. Control frames which are responsible for managing the
+lifecycle of a stream whereas data frames simply transmit data.
 \item[Streaming] Streams are bidirectional and are used to send out of order
@@
 headers rather than the actual content.  If this can be compressed, much
-bandwidth is saved~\cite{binoy}.
+bandwidth is saved~\cite{binoy}. Furthermore, bandwidth for large headers (such
+as cookies) will be saved by assuming headers present for future requests on
+the same stream and in new streams once initialized.
 \end{description}
 
-% TODO: Expand on these for the full paper!
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 their own session layer, Microsoft S+M relies on WebSockets for a session
-layer.  In addition (this is very important), S+M uses HTTP to negotiate the
-protocol upgrade rather than SPDY's use of SSL/TLS to do this same thing. This
-adds quite a bit of latency to beginning the actual communication and is one of
-the reasons that Facebook endorsed SPDY~\cite{fbook}.
+layer.  In addition, S+M uses an HTTP header to negotiate the protocol upgrade
+rather than SPDY's use of the SSL/TLS handshake to do this same thing. This
+adds another round trip after the connection is established, and requires the
+endpoint to analyze the HTTP headers. This is friendly to intermediate proxies
+that do not support S+M, but it quite a bit of latency to beginning the actual
+communication and is one of the reasons that Facebook endorsed SPDY over
+S+M~\cite{fbook}.
 
@@
 Overall, this proposal is aimed at making it easier for network appliances such
-as HTTP reverse-proxies to inspect and route incoming HTTP traffic.
+as HTTP reverse-proxies to inspect and route incoming HTTP traffic. However,
+the Network-Friendly approach has no widely-available client or server
+implementations, so currently it is a much less mature proposal than SPDY.
 

### 2012-12-19 paper/paper.tex
Final changes from Tom

@@
 the specification have been proposed: Google's SPDY, Microsoft's Speed +
-Mobility, and a "Network-Friendly" proposal from a handful of Open Source
+Mobility, and a ``Network-Friendly'' proposal from a handful of Open Source
 authors. The three will be briefly outlined beginning in
@@
 endpoint to analyze the HTTP headers. This is friendly to intermediate proxies
-that do not support S+M, but it quite a bit of latency to beginning the actual
-communication and is one of the reasons that Facebook endorsed SPDY over
-S+M~\cite{fbook}.
+that do not support S+M, but it adds additional latency (1 RTT) to beginning
+the actual communication and is one of the reasons that Facebook endorsed SPDY
+over S+M~\cite{fbook}.
 
@@
 perform an in-depth examination of what is the limiting factor of current
-HTTP/1.1 including a review of literature in the area and a characterization of
-real-world web page asset size distribution in \S\ref{sec:assets} (and
-how we predict the same assets will load if loaded over SPDY). Since SPDY can
-combine asset requests into a single multiplexed TCP connection, we identify
-this as a significant source of performance improvement over HTTP. We will
-perform this by collecting the assets from the top Alexa sites with the Web
-Asset Scraper described in \S\ref{sec:research/scraper}.
+HTTP/1.1 including a characterization of real-world web page asset size
+distribution in \S\ref{sec:assets} and how we predict the same assets will load
+if loaded over SPDY. Since SPDY can combine asset requests into a single
+multiplexed TCP connection, we identify this as a significant source of
+performance improvement over HTTP. We will perform this by collecting the
+assets from the top Alexa sites with the Web Asset Scraper described in
+\S\ref{sec:research/scraper}.
 
@@
 HTTP hostname.
+
+From this data, we analyzed the theoretical benefit of asset combination for SPDY in Section \ref{sec:assets}.
 
@@
 case, 90\% of sites will halve the number of connections by switching to SPDY
-and 40\% could load using one-fifth the connections.
+and 40\% could load using one-fifth the connections while only about 7\% see no
+improvement with SPDY.
 

### 2012-12-19 paper/paper.tex
Update section reference in paper

--- 2012-12-19 paper/paper.tex
@@
 
-\title{An Analysis of the SPDY Protocol as a Candidate for HTTP/2.0}
+\title{An Investigation of the SPDY Protocol}
 \date{\today}
@@
 creator of the stream.  This, in conjunction with server-push (defined next)
-allows for more important assets (images, javascripts, stylesheets, etc.) to be
-sent over the wires first.  An example of the usefulness of this feature is a
-webpage with many images that are unimportant for the actual content and layout
-of the page.  In that case, the images could be given a low priority and sent
-last.
+allows for more important assets to be sent over the wires first.  An example of
+the usefulness of this feature is a webpage with many images that are
+unimportant for the actual content and layout of the page.  In that case, the
+images could be given a low priority and sent last.
 \item[Server-Push] Once a server receives a request for an asset, if it is aware
@@
 The server described in \S\ref{sec:research/server} needs to correctly simulate
-real world webpages. In order to achieve this, we created a web scraping tool
-which scraped websites chosen from the Alexa most popular websites
-list\footnote{\url{http://www.alexa.com}} and recorded the size and number of
-assets into a database.  This database will be accessed by the server upon each
-request in order to determine which data to return.  In order to accurately
-represent the original websites (and the state of the web), we employed a
-headless web browser PhantomJS\footnote{\url{http://phantomjs.org}} which
-mimicked a user's browser and thus requested all assets needed to render a web
-page, even the dynamically loaded ones buried in CSS rules or Javascript.
-
-We desire to record information that will allow us to assess the performance
-characteristics of SPDY for each website we scrape. We recorded, for each
-asset, the source IP we downloaded the asset from, the SSL certificate (if any)
-for the connection on which we downloaded the asset, and the asset's filename
-and filesize.
-
-Not every website supports SSL, and the Alexa list ranks websites by hostname
-combining SSL and non-SSL traffic. Since we are not measuring the time to
-download the asset, we can default to SSL for websites that support it, as we
-can determine useful information about the owner of assets from the SSL
-certificate. For sites that do not support SSL, we will request the non-SSL
-HTTP hostname.
+real world webpages. In order to facilitate this, websites from the Alexa
+rankings\footnote{\url{http://www.alexa.com}} have been scraped and the size and
+number of assets on each recorded.  This database will be accessed by the server
+upon each request in order to determine which data to return.  Great
+consideration was taken to make sure that this data accurately represents the
+state of the web, including executing javascript from each page in a headless
+browser in order to find dynamically loaded assets. This is not part
+of the proposed project as the work has already been completed in conjunction
+with another student.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{SPDY Combination Strategy}
-SPDY's most complex new feature is the ability to multiplex requests for assets
-over a single TCP connection. In this way, a web page's assets can benefit from
-a warmed-up TCP connection which has passed the beginning of the TCP slow start
-algorithm. Since SPDY is currently built atop SSL, SPDY can only combine assets
-with a mutually-agreeable SSL certificate. The assets will be combined into
-separate, interleaved streams over the same TCP connection, thus ideally
-obtaining complete utilization of the connection and the benefit from TCP's
-eventual discovery of an accurate congestion window.
-
-In order to measure the efficiency of SPDY's asset combination, we must
-determine what metric benefits from combining assets. The authors of SPDY claim
-that the main benefit from asset combination is the reduction of network
-connections required~\cite{spdy-whitepaper}.
-
-Although the HTTP/1.1 specification allows for up to two simultaneous
-connections to servers, modern browsers willfully violate it in service of page
-load speed and will happily open up to six connections to each host. Websites
-have also been pushing the limits by creating semantically equivalent hostnames
-for asset servers (i.e. assets1.example.com, assets2.example.com, etc.) so
-browsers will open six connections to each. Thus, browsers may wind up opening
-hundreds of connections immediately upon loading a page -- thus dishonoring the
-intent of TCP slow start.
-
-SPDY's asset combination addresses this. In this section we will measure the
-difference in the number of connections required to load each page under two
-different assumptions: first that site owners could combine all assets with
-mutually-agreeable SSL certificates into one SPDY connection and second that
-site owners would combine all assets served by the same IP address \textit{and}
-with mutually-agreeable SSL certificates into one SPDY connection. Logically,
-the first method is an upper bound for the number of connections we can save,
-we estimate that the second method is more accurate for most websites but is a
-lower bound for websites which employ CDNs or asset host sharding.
-
-\subsection{SSL-only Asset Combination}
-\begin{figure}[h!]
-\centering
-\includegraphics[width=0.4\textwidth,angle=270]{plots/asset_combination_only_ssl_ratio.eps}
-\caption{Connection Ratio -- SSL-only Combination Strategy}
-\label{fig:combination-ssl}
-\end{figure}
-The results in Figure \ref{fig:combination-ssl} assume that all assets
-described by a mutually-compatible SSL certificate are combined into one SPDY
-connection. Two assets have \textit{mutually-compatible} SSL certificates if
-their SSL certificates are valid for the host of the other asset (with either
-the Canonical Name or the Alternative Hostnames). In this way, we
-systematically combine assets by adding them to the largest group with which
-they are compatible. We then compare the number of asset groups (SPDY
-connections) with the number of assets (HTTP connections). The CDF of the ratio
-for the Alexa top 100,000 websites is plotted.
-
-As mentioned previously, this is an upper-bound for multiplexing savings.
-Results nonetheless are dramatic: about 90\% of sites could load using
-one-fifth the connections if combining assets via SPDY.
-
-\subsection{SSL-and-IP Asset Combination}
-\begin{figure}[h!]
-\centering
-\includegraphics[width=0.4\textwidth,angle=270]{plots/asset_combination_ssl_and_ip_ratio.eps}
-\caption{Connection Ratio -- SSL-and-IP Combination Strategy}
-\label{fig:combination-ssl-and-ip}
-\end{figure}
-The results in Figure \ref{fig:combination-ssl-and-ip} assume that all assets
-described by a mutually-compatible SSL certificate and that are downloaded from
-the same IP in practice are combined into one SPDY connection.
-
-Figure \ref{fig:combination-ssl-and-ip} shows that, in the common-to-worst
-case, 90\% of sites will halve the number of connections by switching to SPDY
-and 40\% could load using one-fifth the connections.
-
-\subsection{Connection Sizes}
-\begin{figure}[h!]
-\centering
-\includegraphics[width=0.4\textwidth]{plots/asset_combination_connection_sizes.eps}
-\caption{Connection Sizes After Asset Combination}
-\label{fig:connection-sizes}
-\end{figure}
-
-Figure \ref{fig:connection-sizes} describes the size of connections when all
-assets are combined together as described in the SSL-and-IP combination
-strategy. 70\% of SPDY connections are noticeably larger than HTTP connections,
-up to almost an order of magnitude in some cases. Some assets do not benefit
-from SPDY's combination: small assets like Google Analytics tracking
-Javascript, or external libraries used on web pages such as jQuery. These
-comprise the left part of the SPDY curve.
-
-% we measure two approaches: splitting on SSL cert and IP and simply splitting
-% on SSL cert (as an upper bound for combination). The first method, ssl + ip,
-% is prone to some error due to the use of CDNs confusing our scraping of
-% assets.
+here is where we will discuss the asset measurement stuff.
 

### 2012-12-19 paper/paper.tex
Lots more about spdy

--- 2012-12-19 paper/paper.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The most interesting and likely to succeed proposal, SPDY is rather mature
+The most interesting and likely to succeed proposal, SPDY, is rather mature
 at this point in time, having been implemented in both the most recent Chrome
@@
 
-The most important parts of SPDY as of draft 3 (most recent complete version
-\cite{spdy3}) are framing and streams.
+We will briefly outline the key features of SPDY.
 
-\begin{description}
-\item[Framing Layer] This binary protocol provides a layer on top of a reliable transport
-protocol (recommended to be TCP) and provides a way for HTTP request/response
-pairs to be issued and received out of order over a single transport layer
-connection.  This provides an expected performance improvement of HTTP/1.1 by
-not requiring multiple connections to the host to be made in order to
-parallelize resource acquisition. There are 2 types of frames: control
-frames and data frames. Control frames which are responsible for managing the
-lifecycle of a stream whereas data frames simply transmit data.
-\item[Streaming] Streams are bidirectional and are used to send out of order
-responses to requests. Importantly, streams can have priorities set by the
-creator of the stream.  This, in conjunction with server-push (defined next)
-allows for more important assets (images, javascripts, stylesheets, etc.) to be
-sent over the wires first.  An example of the usefulness of this feature is a
-webpage with many images that are unimportant for the actual content and layout
-of the page.  In that case, the images could be given a low priority and sent
-last.
-\item[Server-Push] Once a server receives a request for an asset, if it is aware
+\subsubsection{Framing Layer}
+This binary protocol is a layer on top of an already reliable transport
+protocol (recommended, but not required, to be SSL+TLS over TCP) and provides a
+way for HTTP requests and responses to be issued and received out of order over
+a single transport layer connection.  This provides an expected performance
+improvement over HTTP/1.1 by allowing connections to warm up after experiencing
+TCP's slow start. Longer connections will have more-accurate congestion window
+sizes, and thus the performance of requests will both be fair for early
+requests and fast for later requests.
+
+The framing layer, while taking steps to improve the speed of connections,
+maintains the semantics of HTTP.  For example, HTTP headers are sent in a
+HEADERS frame, which is a control frame used to convey the headers that would
+be sent over a normal HTTP connection.  There are several types of control
+frames including ones to set-up and tear-down streams (see
+\S\ref{sec:background/spdy/streaming}), to determine the latency of the
+connection, and other logistics as well.  The remainder of the traffic is
+conveyed as data frames.
+
+\subsubsection{Streaming}
+\label{sec:background/spdy/streaming}
+Streams are either unidirectional or bidirectional channels that are used to
+send multiplexed requests and responses.  Stream multiplexing differs from
+HTTP/1.1's pipelining in one important way: HTTP/1.1 enforces a FIFO queue of
+responses to requests whereas many SPDY streams' data may be interleaved.
+SPDY's stream multiplexing suffices to eliminate the inherent head-of-line
+blocking.
+
+Additionally, streams are prioritized by the creator of the stream.  This, in
+conjunction with server-push (defined next) allows for more important assets
+(images, javascripts, stylesheets, etc.) to be sent over the wire first.  An
+example of the usefulness of this feature is a webpage with many images that
+are unimportant for the actual content and layout of the page.  In that case,
+the images could be given a low priority and sent last.
+
+\subsubsection{Server Push}
+Once a server receives a request for an asset, if it is aware
 of closely connected assets, it may send them behind the original response,
 without waiting for the client to request them.  This will pre-populate the
-cache of the client and save a round trip time for each item.
-\item[Header Compression with Dictionary] If there are many small assets on a
-webpage, then a significant portion of the transmitted bytes will be due to HTTP
-headers rather than the actual content.  If this can be compressed, much
-bandwidth is saved~\cite{binoy}. Furthermore, bandwidth for large headers (such
-as cookies) will be saved by assuming headers present for future requests on
-the same stream and in new streams once initialized.
-\end{description}
+cache of the client and save a round trip time for each item. Since server push
+is an optimization for clients, it is up to the clients to make sure that it is
+indeed making their browsing experience faster. For example, the SPDY
+protocol\cite{spdy3} states that ``browsers MUST implement throttles to
+protect against unreasonable push attacks.'' Or, browsers may deny to open a
+server push stream to receive an asset if it is already cached.
+
+\subsubsection{Header Compression with Dictionary}
+If there are many small assets on a webpage, then with HTTP/1.1 a significant
+portion of the transmitted bytes will be due to HTTP headers rather than the
+actual content. One low-hanging fruit for optimization is to compress
+commonly-seen ASCII headers using zlib, which will save lots of of overhead on
+sites with lots of requests~\cite{binoy}.
+
+The SPDY specification includes a pre-seeded zlib dictionary of common HTTP
+headers, so that even the beginnings of connections can benefit from header
+compression.
+
+\subsubsection{Security}
+Although the current SPDY specification does not require mandatory encryption
+over SSL, it is a design goal of SPDY to improve security: The SPDY designers
+``believe that the long-term future of the web depends on a secure network
+connection''\cite{spdy-whitepaper}.
 

### 2012-12-19 paper/paper.tex
Update paper with results of spdyathome

--- 2012-12-19 paper/paper.tex
@@
-\documentclass[11pt,letterpaper,notitlepage]{article}
+\documentclass[10pt,letterpaper,notitlepage]{article}
 
@@
 \usepackage{graphicx}
+\usepackage{multicol}
+\usepackage{float}
 
@@
 HTTP is one of the most widely used application-level protocols. Initially
-written in 1996~\cite{http1rfc}, HTTP was written for a different era of web
+written in 1996~\cite{http1rfc}, it was created for a different era of web
 sites -- before streaming video websites, before asset-heavy web pages, and
@@
 \S\ref{sec:background/spdy} and then the remainder of the paper will focus on
-measurements of the most viable candidate for HTTP/2.0, SPDY.
+measurements of the most viable candidate for HTTP/2.0 -- SPDY.
 
@@
 
-From this data, we analyzed the theoretical benefit of asset combination for SPDY in Section \ref{sec:assets}.
+From this data, we analyzed the theoretical benefit of asset combination for
+SPDY in \S\ref{sec:assets}.
 
@@
 effectiveness of the SPDY protocol. The server can be run from any standard
-machine, but only a single one will be run for the experiment.  The client (the
-``collector'') is the real measurement platform and will be distributed to
+machine, but only two will be run for the experiment.  The client (the
+``collector'') is the real measurement platform and has been distributed to
 volunteers to run in order to test SPDY in a number of different network
-conditions.  The client will collect data and report back to the server
+conditions.  The client collects data and reports back to the server
 anonymous information about how performant the protocol was in addition to
@@
 
-These sites will be selected randomly and made into a list for the client to
+These sites have been selected randomly and made into a list for the client to
 consume. This is a total of 280 sites that run the gamut from representing the
 largest and most frequented sites on the web, down to some of the most obscure.
+The full list of sites used is attached in Appendix~\ref{app:sitelist}.
 
@@
 \item \texttt{/site/<n>} where \texttt{n} is an integer that specifies the index
-of the website simulation that is being accessed.  This will result in the
-server returning fully formed HTML containing assets that map to the proper size
-of the assets from the scraped page.  The rest of the document will be filled
-with random bytes until it is the proper size of the recorded webpage that was
-scraped.
-\item \texttt{/img/<m>} where \texttt{m} is an integer specifying the size of the
+of the site to download. A simple JSON list of each of the assets for a site is
+returned, in addition to random junk to fill the rest of the size of the page.
+
+\item \texttt{/asset/<m>.(c|u)} where \texttt{m} is an integer specifying the size of the
 asset that should be downloaded. So, in the case that we found a 2 MB image on a
 webpage that is being simulated, \texttt{m} will be 2,000,000 and the server
-will return a binary blob of that size. It is possible that this could take into
-account the different compressibility of text to images.  For instance, an asset
+will return a binary blob of that size. The \texttt{c} and \texttt{u} appended
+to the end changes whether the asset should be compressed or not.  For instance, an asset
 that was javascript should have somewhat less random data supplied so that it
@@
 
+Each asset has been determined to either be ``primary'' or ``secondary'' with
+primary assets coming from the original host server itself and secondary coming
+from any other host.  An example of secondary assets would be Google ads.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Thor}
+\label{sec:research/thor}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Both the client and server use the Thor library for HTTP and SPDY communication.
+They share a common core of TCP server and other utilities, so the comparison
+between the two protocols is as close as possible.  The library had to be
+updated to complete its support for SPDY, the version of the library that was
+used for the project can be found at \url{https://github.com/bis12/thor}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The client should be cross platform and easy to run.  The ultimate goal is for
-it to be as simple as downloading and clicking on an executable of some form.
-The client will access each of the tests specified in the list in turn using
-both SPDY and HTTP/1.1 with SSL/TLS and
-record timing information about how long it takes for each request to complete.
-After this step is complete, the client will gather data about its location and
-other considerations in order to return to the server for analysis.  All data
-returned will be presented to the user to approve \textbf{before} being sent
-back.
+The client works in the following way
+\begin{enumerate}
+    \item Connect to the server and download the list of sites to access.
+        Randomize the order of the sites and continue.
+    \item Connect to each of these sites in turn with both HTTP and SPDY clients
+        and download the asset list for each.  The order that HTTP and SPDY
+        connect is randomized each time also.
+    \item Download each of the assets for each site from either the primary or
+        secondary host depending on the original location.
+    \item Once all assets are fetched, or a certain timeout is reached, the TCP
+        connections are torn down and the download of that site is considered
+        complete or ends in an error.
+\end{enumerate}
+Once all of the sites have been downloaded, the results are collected and sent
+back to the server, in addition to recording the IP address and a unique
+identifier for the host so that repeats from the same location and computer can
+be compared.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-here is where we will discuss brian's spdyathome results
+In the following section we will present the results of the data collection and
+a short analysis of the results.
 
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.8\textwidth]{plots/plot1.eps}
+\caption{A simple comparison of dowload times for each site downloaded across
+all collections from all clients.  Positive is time saved by SPDY and negative
+is time added.}
+\label{fig:plot1}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.8\textwidth]{plots/plot9.eps}
+\caption{Similar to Figure~\ref{fig:plot1} except with each site averaged across
+responses.}
+\label{fig:plot9}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.8\textwidth]{plots/plot3.eps}
+\caption{This is identical to Figure~\ref{fig:plot1} except with each response
+averaged across all of their sites.}
+\label{fig:plot3}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.8\textwidth]{plots/plot2.eps}
+\caption{A scatter plot comparing time to download site to the average of the
+    two times it took to download the site.  No correlation appears to be
+present.}
+\label{fig:plot2}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.8\textwidth]{plots/plot8.eps}
+\caption{Scatter of speedup vs the aggregate size in bytes of the site
+downloaded.}
+\label{fig:plot8}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.8\textwidth]{plots/plot12.eps}
+\caption{Scatter of speedup vs the aggregate size in bytes of a site averaged
+across responders.}
+\label{fig:plot12}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.8\textwidth]{plots/plot10.eps}
+\caption{Scatter of speedup vs the number of assets per site
+downloaded.}
+\label{fig:plot10}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.8\textwidth]{plots/plot5.eps}
+\caption{A plot to find if each unique responder with greater than 5 responses
+had a similar result each time.}
+\label{fig:plot5}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.8\textwidth]{plots/plot6.eps}
+\caption{Similar to Figure~\ref{fig:plot1}, but simply in order of response
+    rather than ordered by savings.  This is to find if some sort of confounding
+variable affected the responses across some part of time.}
+\label{fig:plot6}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Final Collections}
+\label{sec:realworld/fc}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+At the time of this analysis there were 41 unique responders from 42 unique IP
+addresses. They combined for a total of 482 responses.  Each test took roughly
+25 minutes to run, so it would be difficult to expand the test further in terms
+of the number of sites downloaded.  The relatively small number of results makes
+it difficult to accurately say anything about each responder in aggregate, but
+this accounts for many tens of thousands of sites downloaded, so trends are
+certainly evident and accurate with regards to the sites.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Analysis}
+\label{sec:realworld/analysis}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Each of the previous plots indicate one of two things
+\begin{itemize}
+    \item  There was no correlation between size of site, number of assets, or
+        any other metric and the speedup from SPDY.
+    \item There was practically no speedup from SPDY
+\end{itemize}
+
+This is contradictory to the results obtained by many other experimenters and
+brings the accuracy of this experiment into question.  Clearly more work needs
+to be done in order to find the cause of this discrepancy.  It seems likely that
+the architecture of the server and client caused greater overheads with
+variability than SPDY could have overcome and this hides the improvements made
+with SPDY. It is also possible that there is an error in the implementation or
+that some aspect of the design of the experiment is fundamentally flawed.  This
+will need to be investigated before possibly going forward with this work.
 % I don't want to remove this wholesale but I don't think it is relevant
@@
 
+\appendix
+\section{List of Sites Used in Experiment}
+\label{app:sitelist}
+\tiny
+\begin{multicols}{4}
+\begin{verbatim}
+https://www.multiply.com
+https://www.google.ru
+http://www.rr.com
+http://www.itimes.com
+http://www.chinanews.com
+http://www.livestream.com
+https://www.google.com.hk
+http://www.facemoods.com
+http://www.ebay.de
+http://www.2345.com
+https://www.google.lk
+https://www.thepiratebay.se
+http://www.hao123.com
+http://www.tmall.com
+https://www.pinterest.com
+https://www.google.com.br
+http://www.slutload.com
+https://www.maxbounty.com
+https://www.thenextweb.com
+https://www.google.es
+http://www.wikihow.com
+http://www.xscores.com
+http://www.2ch.net
+http://www.jrj.com.cn
+https://www.facebook.com
+https://www.apple.com
+https://www.google.com.mx
+http://www.actuweb.net
+https://www.google.co.jp
+https://www.godaddy.com
+https://www.sueddeutsche.de
+http://www.anonym.to
+https://www.fotolia.com
+http://www.imgur.com
+https://www.sourceforge.net
+http://www.espn.go.com
+https://www.google.com
+https://www.utoronto.ca
+https://www.google.co.in
+https://www.mailchimp.com
+http://www.people.com
+https://www.midphase.com
+http://www.okbuy.com
+http://www.yoka.com
+http://www.4399.com
+https://www.amazon.fr
+http://www.livedoor.com
+http://www.xhamster.com
+http://www.tocmai.ro
+http://www.vod.pl
+https://www.citibank.com
+http://www.anonymouse.org
+https://www.youtube.com
+http://www.vporn.com
+http://www.zedo.com
+http://www.lashou.com
+https://www.google.co.nz
+http://www.optymalizacja.com
+https://www.yahoo.com
+http://www.ldlc.com
+http://www.detik.com
+http://www.bunshun.jp
+https://www.freedigitalphotos.net
+http://www.imdb.com
+https://www.odnoklassniki.ru
+https://www.tu-chemnitz.de
+http://www.statigr.am
+http://www.avg.com
+https://www.wordpress.com
+http://www.directlyrics.com
+http://www.bing.com
+https://www.pornhub.com
+https://www.aol.com
+https://www.google.co.kr
+https://www.americangreetings.com
+https://www.adobe.com
+http://www.trklnks.com
+https://www.leagueoflegends.com
+https://www.google.fr
+http://www.funnyjunk.com
+https://www.google.it
+https://www.orkut.com
+http://www.fc2.com
+https://www.egopay.com
+http://www.techcrunch.com
+http://www.ask.com
+https://www.zoopla.co.uk
+https://www.join.me
+https://www.google.ca
+https://www.taz.de
+http://www.soso.com
+https://www.linkedin.com
+https://www.mail2web.com
+http://www.meristation.com
+http://www.godlikeproductions.com
+http://www.neogaf.com
+https://www.google.co.il
+https://www.amazon.de
+http://www.taleo.net
+http://www.babylon.com
+http://www.taobao.com
+http://www.reddit.com
+https://www.amazon.co.jp
+http://www.baidu.com
+http://www.xvideos.com
+http://www.lavanguardia.com
+http://www.ntvmsnbc.com
+http://www.nyaa.eu
+http://www.wcarev.com
+http://www.renren.com
+http://www.rakuten.co.jp
+http://www.neatorama.com
+http://www.alibaba.com
+https://www.live.com
+https://www.sape.ru
+https://www.googleusercontent.com
+http://www.twitpic.com
+https://www.sahibinden.com
+https://www.google.com.pe
+https://www.boards.ie
+https://www.nix.ru
+http://www.jimdo.com
+http://www.lemonde.fr
+http://www.zappos.com
+https://www.smashwords.com
+http://www.engadget.com
+https://www.tumblr.com
+https://www.google.dk
+http://www.oriflame.com
+http://www.ne.jp
+https://www.vk.com
+https://www.adnxs.com
+http://www.majikichi.com
+http://www.youporn.com
+https://www.tagged.com
+http://www.videoweed.es
+https://www.spirithalloween.com
+http://www.bbc.com
+https://www.9gag.com
+http://www.gizmodo.com
+http://www.msn.com
+http://www.linkwithin.com
+http://www.vend-o.com
+http://www.crsky.com
+https://www.twitter.com
+http://www.zedge.net
+https://www.wordpress.org
+http://www.amawebs.com
+http://www.huffingtonpost.com
+http://www.rediff.com
+http://www.wigetmedia.com
+https://www.dailymotion.com
+http://www.yayabay.net
+http://www.sogou.com
+https://www.google.com.tr
+https://www.livejournal.com
+https://www.zopim.com
+http://www.shaadi.com
+http://www.medscape.com
+https://www.flickr.com
+http://www.ahram.org.eg
+http://www.firstclass-download.com
+https://www.conduit.com
+https://www.careerbuilder.com
+https://www.amazon.co.uk
+https://www.backcountry.com
+http://www.zippyshare.com
+https://www.netflix.com
+http://www.daum.net
+http://www.yahoo.co.jp
+http://www.slate.com
+http://www.stackoverflow.com
+http://www.matichon.co.th
+http://www.politiken.dk
+https://www.expedia.com
+https://www.sportsmansguide.com
+http://www.lastfm.es
+https://www.amazon.com
+http://www.tabnak.ir
+https://www.adf.ly
+https://www.blogspot.com
+http://www.welt.de
+https://www.instantcheckmate.com
+http://www.hubpages.com
+http://www.serialu.net
+https://www.google.de
+http://www.clubpenguin.com
+https://www.vodafone.co.uk
+http://www.pcmag.com
+http://www.codecademy.com
+http://www.t.co
+http://www.mlb.com
+https://www.redtube.com
+http://www.ebay.com
+http://www.go.com
+http://www.instagram.com
+http://www.28tlbb.com
+https://www.google.com.au
+http://www.about.com
+https://www.blogger.com
+http://www.extratorrent.com
+http://www.digitaldesire.com
+http://www.youtu.be
+http://www.adultfriendfinder.com
+https://www.ucm.es
+http://www.vcommission.com
+https://www.mail.ru
+http://www.programme-tv.net
+https://www.bbc.co.uk
+http://www.hafeezcentre.pk
+https://www.google.pl
+https://www.google.co.id
+http://www.ebay.co.uk
+http://www.apontador.com.br
+https://www.google.co.uk
+https://www.wikipedia.org
+https://www.web.com
+http://www.ask.fm
+http://www.craigslist.org
+https://www.nokia.com
+http://www.elahmad.com
+https://www.jobrapido.com
+http://www.yesky.com
+http://www.tudou.com
+https://www.hbr.org
+http://www.khl.ru
+http://www.flipora.com
+http://www.babytree.com
+http://www.pcauto.com.cn
+http://www.1uuc.com
+http://www.ifeng.com
+http://www.youku.com
+https://www.uchicago.edu
+http://www.pptv.com
+http://www.formulatv.com
+http://www.searchengines.ru
+http://www.cnn.com
+http://www.fux.com
+http://www.alisoft.com
+http://www.drtuber.com
+http://www.narod.ru
+http://www.msn.com.cn
+http://www.sohu.com
+http://www.globalgrind.com
+http://www.icicibank.com
+http://www.ndtv.com
+http://www.tuan800.com
+http://www.yandex.ru
+http://www.grindtv.com
+http://www.w3schools.com
+https://www.paypal.com
+http://www.ccb.com
+http://www.uol.com.br
+http://www.mywebsearch.com
+http://www.porntube.com
+http://www.tinypic.com
+http://www.hypergames.net
+89909 http://www.tianya.cn
+http://www.126.com
+http://www.newbigtube.com
+https://www.microsoft.com
+http://www.chinaren.com
+http://www.laptopmag.com
+http://www.biglion.ru
+http://www.weibo.com
+http://www.xunlei.com
+http://www.livejasmin.com
+http://www.super.cz
+https://www.fandango.com
+\end{verbatim}
+\end{multicols}
 \end{document}

### 2012-12-19 paper/paper.tex
Fin

@@
 will need to be investigated before possibly going forward with this work.
+
+\section{Conclusion}
+\label{sec:conlusion}
+In this paper we have outlined the three candidates for HTTP/2.0: SPDY,
+Speed+Mobility, and Network Friendly. We found potential for improvement from
+SPDY based on our measurements of the web, but when we pushed further, no
+improvement could be found.
+
 % I don't want to remove this wholesale but I don't think it is relevant
@@
 \appendix
-\section{List of Sites Used in Experiment}
+\section{Sites Used in Experiment}
 \label{app:sitelist}
